Location of Shrimp Farms

### 2021-03-23 marine_mapping_archive_v1/shrimp/shrimp_farms/STEP2_shrimp_farm_locations.Rmd
Finished reorganizing data

Now we will map the remaining countries with shrimp farms. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or 
 dataset (such as FAO or a research paper)
 - If there are not exact locations or comprehensive locations, find the number of farms. 
 - If there is no information at all, note it. We will gapfill later.

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1).

5: Comprehensive number of exact farms

4: Subset of exact locations, need to add a specific number of farms to existing locations. 
  - country|species|farm locations
  - country|species|additional points

3: A specific number of farms are known, but no locations 
 - country|species|additional points

2.5: A specific number of farms that are not comprehensive, so we will have to gapfill on top of those, if necessary. 
 - country, species, n_existing_points

2: Exact locations are a subset of total farms. But the number of total farms are unknown. Need to be gapfilled by tonnage.

1: No information on number of farms at all. Need to be gapfilled by tonnage. 
 - country|species|# additional farms (this will be NA)

## Read in ASC data
https://gis.asc-aqua.org/arcgis_app/
Maps from ASC

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c) %>%
  mutate(data_quality = 5)

## save farm location
write.csv(farms_all_fin, here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv"), row.names = FALSE)

@@

Now we need to map for each country, and assign a flag for gapfilling which will be completed later. I will start with all of the countries list in the ASC data.

# Indonesia 
Current data is from ASC, only 5 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of Indonesia. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_idn <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "IDN") %>%
  mutate(data_quality = 2)

write_csv(farms_idn, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_idn.csv"))

# New Caledonia

Current data is from ASC, only 2 farms, so probably not comprehensive. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_ncl <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "NCL") %>%
  mutate(data_quality = 2)

write_csv(farms_ncl, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ncl.csv"))

# Mexico 
Current data is from ASC, only 11 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of Mexico. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_mex <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "MEX") %>%
  mutate(data_quality = 2)

write_csv(farms_mex, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_mex.csv"))

# Venezuela 
Current data is from ASC, only 11 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of Venezuela. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_ven <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "VEN") %>%
  mutate(data_quality = 2)

write_csv(farms_ven, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ven.csv"))

# India

Current data is from ASC, only 104 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of India. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_ind <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "IND") %>%
  mutate(data_quality = 2)

write_csv(farms_ind, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ind.csv"))

# Viet Nam

Current data is from ASC, only 173 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of viet nam. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_vnm <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "VNM") %>%
  mutate(data_quality = 2)

write_csv(farms_vnm, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_vnm.csv"))

# Ecuador

Current data is from ASC, which is likely not comprehensive.

The FAO states this: 
"Until 1998 (the last period for which statistics on the subject area available), the Under-Ministry of Fisheries Resources registered 2 006 shrimp industries, 312 larvae hatcheries, 21 feed manufacturing plants and 76 processing plants."

It is hard to tell how many shrimp farms are actually in Ecuador. I do think the ASC number is a good number, but it is probably not comprehensive given the amount of production from Ecuador. Data quality = 2.

```{r}
farms_ecu <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "ECU") %>%
  mutate(data_quality = 2)

write_csv(farms_ecu, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_ecu.csv"))

# Honduras

Current data is from ASC, only 20 farms, so probably not comprehensive. There are likely many more farms than this. The FAO states there are many smal lscale shrimp farms tat are not documented, so it is impossible to tell how many there are from current information. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_hnd <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "HND") %>%
  mutate(data_quality = 2)

write_csv(farms_hnd, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_hnd.csv"))

# China

Current data is from ASC, only 4 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of China. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_chn <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "CHN") %>%
  mutate(data_quality = 2)

write_csv(farms_chn, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))

# Thailand
Current data is from ASC, only 18 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of Thailand. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_tha <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "THA") %>%
  mutate(data_quality = 2)

write_csv(farms_tha, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_tha.csv"))

# Madagasgar

Need to add 4 points to existing 2 (a final total of 6 points)

From FAO:
For marine aquaculture, the six shrimp breeding companies created 4 325 full-time jobs, 4 267 of which were for local people and 58 for expatriates (Anon. 2005b). These 4 325 full-time jobs were distributed as follows: 90 mariners, 1 072 in the processing plant, 400 in administration, 267 in hatcheries, 2 114 in farms, and 382 in other areas. This kind of shrimp farming also created 30 000 indirect jobs. Seaweed culture was being practised by 126 farmers.

Data quality = 4

```{r}
farms_mdg <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "MDG") %>%
  mutate(data_quality = 4)

write_csv(farms_mdg, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_mdg.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
mdg_additional <- data.frame(iso3c = "MDG", type = "shrimp", num_additional_farms = 4, data_quality = 4, total_farms = 6)
write.csv(mdg_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_mdg.csv"), row.names = FALSE)
```

# Panama
Current data is from ASC, only 1 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of Panama. There are likely more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_pan <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "PAN") %>%
  mutate(data_quality = 2)

write_csv(farms_pan, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_pan.csv"))

# Bangladesh
Current data is from ASC, only 1 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of Bangladesh There are likely more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_bgd <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "BGD") %>%
  mutate(data_quality = 2)

write_csv(farms_bgd, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_bgd.csv"))

# Guatemala

Need to add 19 points to existing 3 (a final total of 22 points)

Current data is from the ASC, which is not comprehensive.

http://www.fao.org/fishery/countrysector/naso_guatemala/en
 - “There are 34 shrimp farms of which 22 are active and 12 inactive.”

```{r}
farms_gtm <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "GTM") %>%
  mutate(data_quality = 4)

write_csv(farms_gtm, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_gtm.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
gtm_additional <- data.frame(iso3c = "GTM", type = "shrimp", num_additional_farms = 19, data_quality = 4, total_farms = 22)
write.csv(gtm_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_gtm.csv"), row.names = FALSE)
```

# Nicaragua

Seafood watch claims there is no available information other than the ASC farms. 
https://seafood.ocean.org/wp-content/uploads/2018/12/MBA_SeafoodWatch_FarmedShrimp_Nicaragua_Report.pdf

Current data is from ASC, only 2 farms, so definitely not comprehensive, just a drop in the bucket compared to the produciton of Nicaragua. There are likely more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_nic <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "NIC") %>%
  mutate(data_quality = 2)

write_csv(farms_nic, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_nic.csv"))

# Australia
Current data is from ASC, only 2 farms, so probably not comprehensive. There are likely more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
farms_aus <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "AUS") %>%
  mutate(data_quality = 2)

write_csv(farms_aus, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_aus.csv"))

# Peru

Need to add 71 points to existing 1 (a final total of 72 points).

Current data is a subset of farms from ASC. There is currently 1 point.

https://seafood-tip.com/sourcing-intelligence/countries/peru/shrimp/
 - “22 Medium and large corporate farms are responsible for the majority of shrimp exports, while 50 small-scale farmers mainly produce for the domestic market”

```{r}
farms_per <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "PER") %>%
  mutate(data_quality = 4)

write_csv(farms_per, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_per.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
per_additional <- data.frame(iso3c = "PER", type = "shrimp", num_additional_farms = 71, data_quality = 4, total_farms = 72)
write.csv(per_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_per.csv"), row.names = FALSE)
```

# Colombia 
Need to add 19 points to existing 1 (a final total of 20 points)

Current data is from the ASC, which is a subset of points.

http://www.fao.org/fishery/countrysector/naso_colombia/en
 - “The shrimp farming industry operates nine maturation laboratories, eighteen larval culture laboratories, twenty shrimp farms and seven processing plants. All of them employ qualified labour force, made up of professionals and expert technicians in their respective field of work (Minagricultura and ACUANAL, 2002).”

```{r}
farms_col <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "COL") %>%
  mutate(data_quality = 4)

write_csv(farms_col, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_col.csv"))

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
col_additional <- data.frame(iso3c = "COL", type = "shrimp", num_additional_farms = 19, data_quality = 4, total_farms = 20)
write.csv(col_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_col.csv"), row.names = FALSE)
```

@@

farms_blz <- data.frame(lat=c(17.565826428687156, 17.088537866900786, 16.996401736714773, 16.91300830350531, 16.77084262777864, 16.664824857803115, 16.56115563573352, 16.460774477225453, 16.43434608053408),
                        lon=c(-88.30446591534489, -88.3141468760761, -88.28891758186664, -88.30401223336973, -88.3358879288162, -88.39502139821094, -88.41922498380852, -88.43760570009555, -88.4650001965993),
                        subregion = c("Nova Ladyville Shrimp Farm", "Paradise Shrimp Farm", "Melinda Mariculture Limited", "Triton Mariculture", "Haney's Shrimp Farm", "Belize Aquaculture Limited", "Texmar Shrimp Farm", "Nova Toledo Shrimp Farm", "Toledo Fish Farm")) %>%
  mutate(iso3c = "BLZ") %>%
  mutate(data_quality = 5)

# now join with the ASC data
farms_blz_asc <- read.csv(here("marine/shrimp/shrimp_farms/data/ASC_shrimp_farm_lat_lon.csv")) %>%
  dplyr::filter(iso3c == "BLZ")

farms_blz_total <- full_join(farms_blz, farms_blz_asc)

write_csv(farms_blz, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_blz.csv"))

## visualize it 
farms_blz <-  st_as_sf(farms_blz_total, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

@@

# Brazil
 - Has a map of major shrimp farming locations (from 2002): http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.200.2425&rep=rep1&type=pdf
 - Also has a table of area per state.

@@

 - Because this source doesn't hav especifics on numbers of farms or where they are located, I will treat this as no information that will need to be fully gapfilled.

```{r}
bra_gf <- data.frame(iso3c = "BRA", type = "shrimp", num_additional_farms = NA, data_quality = 1)
write_csv(bra_gf, here("marine/shrimp/shrimp_farms/data/no_info_1/gf_bra.csv")) 
```

@@

 - Because this is just data from one shrimp company in the Brunei, we will assume this is not comprehensive, and we will need to gapfill the remaining tonnage.

```{r}
farms_brn <- data.frame(lat=c(4.716865, 4.722253, 4.742089, 4.761099, 4.781321, 4.970718),
                        lon=c(114.535353, 114.541318, 114.574539, 114.610558, 114.607222, 115.043816),
                        area_ha = c(14, 40, 92, 0.4, 200, 51.471511)) %>%
  mutate(iso3c = "BRN") %>%
  mutate(data_quality = 2)

write_csv(farms_brn, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_brn.csv"))

@@

# Cambodia 
 - There is a table in here. But it only has area estimates: https://clarklabs.org/wp-content/uploads/2019/01/Aquaculture-and-Coastal-Habitats-Report-No1.docx.pdf

@@

 - Because this source doesn't hav especifics on numbers of farms or where they are located, I will treat this as no information that will need to be fully gapfilled.

```{r}
khm_gf <- data.frame(iso3c = "KHM", type = "shrimp", num_additional_farms = NA, data_quality = 1)
write_csv(khm_gf, here("marine/shrimp/shrimp_farms/data/no_info_1/gf_khm.csv")) 
```

# Costa Rica
 - This says there are 90 shrimp producers in Costa Rica. all located in Puntarenas and Guanacaste provinces: http://www.fao.org/fishery/countrysector/naso_costarica/en
 - We will place 90 farms into suitable locations along Costa Rica's coast.

@@

```{r}
farms_cri <- data.frame(iso3c = "CRI", type = "shrimp", num_additional_farms = 90, data_quality = 3)

write_csv(farms_cri, here("marine/shrimp/shrimp_farms/data/known_number_farms_3/farms_cri.csv"))

@@

“Production of market-size shrimp takes place in 5 state-owned farms that are located at Cuba’s southern coast (which is less prone to the impact of storms than the country’s northern coast)”

This means that we need to place 3 more farms in Cuba.

```{r}
farms_cub <- data.frame(lat=c(19.841789, 20.047065),
                        lon=c(-77.737212, -77.593449),
                        area_ha = c(NA, NA)) %>%
  mutate(iso3c = "CUB") %>%
  mutate(data_quality = 4)

write_csv(farms_cub, here("marine/shrimp/shrimp_farms/data/known_farm_sites_2_4_5/farms_cub.csv"))

@@

mapview(farms_cub)

## Now we will make a file that tells us the number of additional farms that need to be added to be comprehensive
cub_additional <- data.frame(iso3c = "CUB", type = "shrimp", num_additional_farms = 3, data_quality = 4, total_farms = 5)
write.csv(cub_additional, here("marine/shrimp/shrimp_farms/data/subset_known_add_points_4/add_farms_cub.csv"), row.names = FALSE)
```

# El Salvador 
http://www.fao.org/fishery/countrysector/naso_elsalvador/en

 = “According to the aquaculture method and the scale of production, aquaculture production units are distributed as follows: 15 production units of tilapia cages, 26 reservoirs for household consumption, 50 small and medium scale units, 1 industrial scale unit; 2 ornamental fish production units, 23 units of fresh water prawns, and 39 marine shrimp farms.”

 - I must’ve missed this my first lit review, so we will place 39 marine shrimp farms in suitable locations along the El Salvador coast.

@@

```{r}
farms_slv <- data.frame(iso3c = "SLV", type = "shrimp", num_additional_farms = 39, data_quality = 3)

write_csv(farms_slv, here("marine/shrimp/shrimp_farms/data/known_number_farms_3/farms_slv.csv"))
```

>>>>

Now we will map the remaining countries with shrimp farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

For each point, we will add a column for "data quality". It will be scored as very good (5), good (4), fair (3), bad (2), and very bad (1). 
 5: Very Good qualifications - Locations taken from leases, or from a map with specific locations
   - Must not intersect with land mask
   - "Land mask"

4: Good qualifications - Locations are projected or it is a only sample of total locations
   - Must not intersect with land mask
   - "Land mask"

3: Fair qualifications - A specific number of farms are placed on the coast, without knowing exact locations. 
   - Must be allocated spatially
   - Must not intersect with land mask
   - Flagged as "Allocate spatially"

2: Bad qualifications -  We know that aquaculture is limited to a specific subregion/state, but do not know how many or where the farms are. 
   - Must be allocated using suitability analysis.
   - Flagged as 2 and "state/province suitability"

1: Very Bad qualifications - No data at all.
   - Must be allocated using suitability analysis.
   - Flagged as 1 and "country suitability"

@@

farms_all_fin <- data.frame(do.call(rbind, st_geometry(all_pts_latlon))) 
names(farms_all_fin) <- c("lon", "lat")
farms_all_fin <- farms_all_fin %>%
  cbind(iso3c = all_pts_latlon$iso3c) %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land mask")

## save farm location
write.csv(farms_all_fin, here("marine/shrimp/shrimp_farms/data/farm_sites/ASC_shrimp_farm_lat_lon.csv"), row.names = FALSE)

@@

@@

farms_blz <- data.frame(lat=c(17.565826428687156, 17.088537866900786, 16.996401736714773, 16.91300830350531, 16.77084262777864, 16.664824857803115, 16.56115563573352, 16.460774477225453, 16.43434608053408),
                        lon=c(-88.30446591534489, -88.3141468760761, -88.28891758186664, -88.30401223336973, -88.3358879288162, -88.39502139821094, -88.41922498380852, -88.43760570009555, -88.4650001965993),
                        subregion = c("Nova Ladyville Shrimp Farm", "Paradise Shrimp Farm", "Melinda Mariculture Limited", "Triton Mariculture", "Haney's Shrimp Farm", "Belize Aquaculture Limited", "Texmar Shrimp Farm", "Nova Toledo Shrimp Farm", "Toledo Fish Farm")) %>%
  mutate(iso3c = "BLZ") %>%
  mutate(data_quality = 5) %>%
  mutate(action_needed = "Land Mask")

write_csv(farms_blz, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_blz.csv"))

## visualize it 
farms_blz <-  st_as_sf(farms_blz, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

@@

# Brazil
 - Has a map of major shrimp farming locations (from 2002): http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.200.2425&rep=rep1&type=pdf
 - Also has a table of number of farms and area per state. I will just place one point at on each state, and add up the area listed in the table.

 - Pará: -0.952238, -48.466718: 70 hectares
 - Maranhão: -2.365963, -44.263791: 64 hectares
 - Piauí: -2.859201, -41.551117: 425 hectares
 - Ceará: -3.646201, -38.627546: 982 hectares
 - Rio G. do Norte: -5.100375, -35.667111: 1752 hectares
 - Paraíba: -7.089602, -34.818058: 420 hectares
 - Pernambuco: -8.115310, -34.840892: 670 hectares
 - Alagoas: -9.700209, -35.739681: 20 hectares
 - Sergipe: -10.991527, -37.030238: 47 hectares
 - Bahia: -13.046432, -38.515139: 1510 hectares
 - São Paulo: inland, don't include
 - Paraná: -25.535885, -48.268714: 50 hectares
 - Sta. Catarina: -27.505551, -48.393581: 200 hectares

@@

```{r}
farms_bra <- data.frame(lat=c(-0.952238, -2.365963, -2.859201, -3.646201, -5.100375,  -7.089602, -8.115310, -9.700209, -10.991527, -13.046432, -25.535885, -27.505551),
                        lon=c(-48.466718, -44.263791, -41.551117, -38.627546, -35.667111, -34.818058, -34.840892, -35.739681, -37.030238, -38.515139, -48.268714, -48.393581),
                        area_ha = c(70, 64, 425, 982, 1752, 420, 670, 20, 47, 1510, 50, 200),
                        subregion = c("Pará", "Maranhão", "Piauí", "Ceará", "Rio Grande do Norte", "Paraíba", "Pernambuco", "Alagoas", "Sergipe", "Bahia", "Paraná", "Santa Catarina")) %>%
  mutate(iso3c = "BRA") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

write_csv(farms_bra, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_bra.csv"))

## visualize it 
farms_bra <-  st_as_sf(farms_bra, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_bra)
```

@@

```{r}
farms_brn <- data.frame(lat=c(4.716865, 4.722253, 4.742089, 4.761099, 4.781321, 4.970718),
                        lon=c(114.535353, 114.541318, 114.574539, 114.610558, 114.607222, 115.043816),
                        area_ha = c(14, 40, 92, 0.4, 200, 51.471511)) %>%
  mutate(iso3c = "BRN") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_brn, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_brn.csv"))

@@

# Cambodia 
 - There is a table in here. We will just place a point on the coast for each of these coastal places, and use the area noted in the paper later if needed. If the province is not coastal, it will not be placed on the map: https://clarklabs.org/wp-content/uploads/2019/01/Aquaculture-and-Coastal-Habitats-Report-No1.docx.pdf

 - Kampot: 10.559329, 104.213349: 1516 hectares
 - Kep: 10.449929, 104.404934: 459 hectare
 - Koh Kong: 11.740932, 102.898284: 26762 hectare
 - Preah Sihanouk: 10.743017, 103.653332: 6388 hectares
 - Pursat: Inland, don't include
 - Svay Rieng: Inland, don't include
 - Takeo: Inland, don't include

@@

farms_khm <- data.frame(lat=c(10.554565566560438, 10.4453604331596, 11.7394298718815, 10.744571388081424),
                        lon=c(104.21523743679825, 104.404236625661, 102.8937349735425, 103.65371151346486),
                        area_ha = c(1516, 459, 26762, 6388), subregion = c("Kampot", "Kep", "Koh Kong", "Preah Sihanouk")) %>%
  mutate(iso3c = "KHM") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

write_csv(farms_khm, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_khm.csv"))

## visualize it 
farms_khm <-  st_as_sf(farms_khm, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_khm)
```

# Costa Rica
 - This says there are 90 shrimp producers in Costa Rica. all located in Puntarenas and Guanacaste provinces: http://www.fao.org/fishery/countrysector/naso_costarica/en
 - I will equally allocate the farm points along the coast line of these two provinces (90 farms total).

@@

```{r}
provinces <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/Costa_rica/gadm36_CRI_1.shp"))
mapview(provinces)

guana <- provinces  %>%
  dplyr::filter(NAME_1 %in% c("Guanacaste"))

punta <- provinces  %>%
  dplyr::filter(NAME_1 %in% c("Puntarenas"))

mapview(guana)
mapview(punta)

## First do Guanacaste
guana_world_crs <- st_transform(guana, crs(coast_raw))

guana_world_crop <- st_crop(coast_raw, guana_world_crs) %>% ## crop to costa rica extent 
  filter(FID %in% c(245921:245926)) %>% ## filter for the correct coastline 
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
mapview(guana_world_crop)

g_meters <- st_transform(guana_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(g_meters)

buff <- st_buffer(g_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(guana_world_crop))
mapview(buffer_outline_fixed)

costa_rica <- ne_countries(scale = 10, country = "Costa Rica", returnclass = "sf")
mapview(costa_rica)

linestring_fix <- st_difference(buffer_outline_fixed, costa_rica) ## now grab only the outline 
mapview(linestring_fix)

guana_crop <- as(linestring_fix, "Spatial")
mapview(guana_crop)

guana_points_lines <- sample.line(guana_crop, n = 55) ## equally place the number of farms along the coastline

guana_points <- st_as_sf(guana_points_lines) %>%
  mutate(new_id = 1:55) %>%
  filter(new_id %in% c(5:49))
mapview(guana_points)

guana_pts <- st_centroid(guana_points)

guana_pts_latlon <- st_transform(guana_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_guana <- data.frame(do.call(rbind, st_geometry(guana_pts_latlon)))
names(farms_guana) <- c("lon", "lat")

farms_guana_final <- farms_guana %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially") %>%
  mutate(subregion = "Guanacaste")

## Now do puntarenas
punta_world_crs <- st_transform(punta, crs(coast_raw))

punta_world_crop <- st_crop(coast_raw, punta_world_crs) %>% ## crop to costa rica extent 
  filter(FID %in% c(245909:245917, 245919:245920)) %>% ## filter for the correct coastline 
  mutate(new_id = 1) %>%
  group_by(new_id) %>%
  summarise(geometry = st_union(geometry)) %>%
  ungroup()
mapview(punta_world_crop)

p_meters <- st_transform(punta_world_crop, crs = 7801) ## transform to a crs that can buffer in meters 
mapview(p_meters)

buff <- st_buffer(p_meters, dist = 7000) # buffer out to XX km so that we can place points along a line 1 km from the coastline
mapview(buff)

linestring <- st_cast(buff, "LINESTRING") ## make a line string so we can filter for the outline 
mapview(linestring)

## now reproject back to original 
buffer_outline_fixed <- st_transform(linestring, crs = crs(punta_world_crop))
mapview(buffer_outline_fixed)

buffer_outlined_fixed2 <- buffer_outline_fixed[1, ]
mapview(buffer_outlined_fixed2)

costa_rica <- ne_countries(scale = 10, country = "Costa Rica", returnclass = "sf")
mapview(costa_rica)

linestring_fix <- st_difference(buffer_outlined_fixed2, costa_rica) ## now grab only the outline 
mapview(linestring_fix)

punta_crop <- as(linestring_fix, "Spatial")
mapview(punta_crop)

punta_points_lines <- sample.line(punta_crop, n = 60) ## equally place the number of farms along the coastline

punta_points <- st_as_sf(punta_points_lines) %>%
  mutate(new_id = 1:60) %>%
  filter(new_id %in% c(2:46))
mapview(punta_points)

punta_pts <- st_centroid(punta_points)

punta_pts_latlon <- st_transform(punta_pts, crs = "+init=epsg:4326") %>%
  dplyr::select(geometry)

farms_punta <- data.frame(do.call(rbind, st_geometry(punta_pts_latlon)))
names(farms_punta) <- c("lon", "lat")

farms_punta_final <- farms_punta %>%
  mutate(iso3c = "CRI") %>%
  mutate(data_quality = 3) %>%
  mutate(action_needed = "Allocate spatially") %>%
  mutate(subregion = "Puntarenas")

farms_cri_final <- rbind(farms_punta_final, farms_guana_final)

## visualize it 
farms_cri <-  st_as_sf(farms_cri_final, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_cri)

## write to farms folder 
write_csv(farms_cri_final, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_cri.csv"))

@@

```{r}
farms_cub <- data.frame(lat=c(19.841789, 20.047065),
                        lon=c(-77.737212, -77.593449),
                        area_ha = c(NA, NA)) %>%
  mutate(iso3c = "CUB") %>%
  mutate(data_quality = 4) %>%
  mutate(action_needed = "Land mask")

write_csv(farms_cub, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_cub.csv"))

@@

mapview(farms_cub)
```

# El Salvador 
 - Could use the table here. We would just assign one farm per each city listed: http://www.fao.org/fishery/countrysector/naso_elsalvador/en

 - Ahuachapan: seems inland
 - Sonsonate: seems inland
 - La Paz: 13.336985, -89.014470: 8.2 hectares
 - Usulután: seems inland
 - La Unión: 13.354459, -87.863771: 50 hectares

@@

```{r}
farms_slv <- data.frame(lat=c(13.336985, 13.354459),
                        lon=c(-89.014470, -87.863771),
                        area_ha = c(8.2, 50),
                        subregion = c("La Paz", "La Unión")) %>%
  mutate(iso3c = "SLV") %>%
  mutate(data_quality = 2) %>%
  mutate(action_needed = "state/province based suitability")

write_csv(farms_slv, here("marine/shrimp/shrimp_farms/data/farm_sites/farms_slv.csv"))
